Assessment and implementation of resource road simulation methods for projection of cumulative effects of disturbance on wildlife

### 2023-01-18 analysis/paper/paper.Rmd
some more fixs for cutOnly

# get proportional difference from observed
prop_dif <- projected_values %>% 
  left_join(observed_values %>% select(areaMean, metric, response),
            by = c("areaMean", "metric"), 
            suffix = c("_proj", "_obs")) %>% 
  mutate(prop_dif = (response_proj-response_obs)/response_obs,
         areaMean = factor(areaMean, labels = c("Cutblocks", "Overall"))) %>% 
  mutate(prop_dif = ifelse(sampleDens == "Cutblocks only" & 
                             metric %in% c("Road\ndensity", "Road\npresence",
                                           "Distance\nto road"),
                           NA_real_, prop_dif))

@@

# performance table
perf_tbl <- matchData_sum %>% 
  pivot_wider(c(metric, sampleDens), names_from = agreement, 
              values_from = count) %>% 
  mutate(sensitivity = `Agree roaded`/(`Agree roaded` + `False negative`),
         precision = `Agree roaded`/(`Agree roaded` + `False positive`),
         F_measure = (2*precision*sensitivity)/(precision+sensitivity)) %>% 
  select(metric, sampleDens, sensitivity, precision, F_measure)

perf_tbl_rng <- perf_tbl %>% group_by(metric) %>% 
  summarise(rng_F = range(F_measure) %>% round(3) %>% paste0(collapse = " - "), .groups = "drop") %>% pull(rng_F, name = metric)

>>>>

# get proportional difference from observed
prop_dif <- projected_values %>% 
  left_join(observed_values %>% select(areaMean, metric, response),
            by = c("areaMean", "metric"), 
            suffix = c("_proj", "_obs")) %>% 
  mutate(prop_dif = (response_proj-response_obs)/response_obs,
         areaMean = factor(areaMean, labels = c("Cutblocks", "Overall")))

@@

# performance table
perf_tbl <- matchData_sum %>% 
  pivot_wider(c(metric, sampleDens), names_from = agreement, 
              values_from = count, values_fill = 0) %>% 
  mutate(sensitivity = `Agree roaded`/(`Agree roaded` + `False negative`),
         precision = `Agree roaded`/(`Agree roaded` + `False positive`),
         F_measure = (2*precision*sensitivity)/(precision+sensitivity)) %>% 
  select(metric, sampleDens, sensitivity, precision, F_measure)

perf_tbl_rng <- perf_tbl %>% group_by(metric) %>% 
  summarise(rng_F = range(F_measure, na.rm = TRUE) %>% round(3) %>% paste0(collapse = " - "), .groups = "drop") %>% pull(rng_F, name = metric)
